---
title: "report"
date: today
format: html
editor: visual
number-sections: true
toc: true
toc-title: Contents
---

# Study objective

x

## Questions

x

# Setup

First, we load required R packages, set some options, and initialise the cache.

```{r}
#| code-fold: true
#| code-summary: "Loading packages and setting options"
#| file: R/0_init.R
#| message: false
#| warning: false
```

# Pre-data

## Concept

x

## Causal model

### Module 1: x {#sec-simmod1}

x

#### Assumptions

| Assumption | Justification |
|------------|---------------|
| x          | x             |

: Assumptions of simulation module "Outcome misclassification without predictor" {#tbl-simmod1-asmp}

#### Variables

| Variable | Description |
|----------|-------------|
| $x$      | x           |

: Variables of simulation module "Outcome misclassification without predictor" {#tbl-simmod1-var}

#### Parameters

| Parameter | Description |
|-----------|-------------|
| $x$       | x           |

: Parameters of simulation module "Outcome misclassification without predictor" {#tbl-simmod1-par}

#### Technical details

$$
\begin{align}
x &\sim Bernoulli(x) \\
y &= x
\end{align}
$$

```{dot}
//| label: fig-graph-simmod1
//| fig-cap: 'Graph of simulation module "x" (Ellipse: Variable, Diamond: Parameter)'
//| fig-height: 2
digraph sim_mod_gr_1 {
  rankdir = LR
  bgcolor = "transparent"
  
  from_other_module [label = <From other<SUB>module</SUB>>, shape = box]      
  var [label = <Var<SUB>1</SUB>>]      
  par [label = <A parameter>, shape = diamond]      
  
  from_other_module -> var   
  par -> var 
}
```

#### Code

```{r}
#| code-fold: true
#| code-summary: "Create module 'x' in simcausal"
#| file: R/pre_1_1_x.R
```

## Simulation

### Testing

First, we test if the simulation modules have been implemented correctly. For this, we simulate some data based on pre-specified parameter values and evaluate if we can recover the expected values.

#### Module 1: x

x

### Simulation 1: x

x (see @sec-simmod1)

# Data

## Prepare data

x

## Descriptives

x

## Multiple Imputation

x

# Post-data

x

# References {.unnumbered}
